External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-10-31 CVPR2017_Review_Unified.tex
add

%%%%%%%%% ABSTRACT
\begin{abstract}
For image denoising problem, the external and internal priors are playing key roles in many different methods. External priors learn from external images to restore noisy images while internal ones exploit priors of given images for denoising. The external priors are more generative and efficient on recovering structure s existing in most images while the internal priors are more adaptive on recovering details existed in given noisy images. In this paper, we propose to employ the external patch group prior of images to guide the clustering of internal patch groups, and develop an external dictionary guided internal orthogonal dictionary learning algorithm for real image denoising. The internal orthogonal dictionary learning process has closed-form solutions and hence very efficient for image denoising. We perform extensive experiments on dozens of real noisy images captured by different cameras and camera settings under controlled indoor or uncontrolled outdoor lighting conditions. The results demonstrate that the proposed method achieves better performance than other state-of-the-art methods on real image denoising. 
\end{abstract}
%Though these methods are very effective in Gaussian noise removal, the noise in real images are signal dependent and more complex than Gaussian noise. Therefore, only exploiting the external or internal priors are not enough for real image denoising.

@@

We compare the above mentioned methods on the 60 cropped images from \cite{crosschannel2016}. The average PSNR and speed of these methods are listed in Table \ref{tab1}. It can be seen that our proposed method achieves better PSNR results than the methods of "External" and "Internal". The speed of our proposed method is much faster than the "Internal" method while a little slower than the "External" method. We also compare the visual quality of the denoised images by these methods. From the results listed in Figure \ref{fig2} and Figure \ref{fig3}, we can see that the "External" method is good at recovering structures (Figure \ref{fig2}) while the "Internal" method is good at recovering internal complex textures (Figure \ref{fig3}). And by utilizing both the external and internal priors, our proposed method can recover well both the structures and textures. Noted that the noisy images in Figures \ref{fig2} and \ref{fig3} are cropped from the same image captured by Nikon D600 at ISO $=3200$ in \cite{crosschannel2016}. Hence, the differences on PSNR and visual quality among these methods only depends on the contents of the cropped images.

\begin{table}
\caption{Average PSNR (dB) results and Run Time (seconds) of the External, the Internal, and our proposed methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
\label{tab1}
\vspace{-3mm}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{External} &\textbf{Internal} &\textbf{Ours}  
\\
\hline
PSNR & 34.51 & 38.21 & 38.07 & \textbf{38.75} 
\\
\hline
Time & | &  ?  & 706.63 & 58.47
\\
\hline
\end{tabular}
\end{center}\vspace{-6mm}
\end{table}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Image priors (e.g., sparsity, self-similarity) are playing key roles in image denoising problem. External priors are priors learned from external (usually clean) images while internal priors are learned from the given noisy image. The external priors are more generative on recovering structures in images while the internal priors are more adaptive on recovering textures and details in given noisy image. In this paper, we propose an algorithm of external priors guided internal priors learning for real image denoising. Specifically, the external priors are learned on patch groups (PGs) from external images via Gaussian Mixture Model, and employed to guide the clustering and orthogonal dictionary learning of PGs from the given noisy image. The orthogonal dictionary learning has closed-form solutions and the image denoising is simultaneously performed with the learning process. We perform extensive experiments on real image denoising, in which the noisy images are captured by different cameras and camera settings under controlled indoor or uncontrolled outdoor lighting conditions. The results on PSNR and visual quality demonstrate that the proposed method achieves better performance than other state-of-the-art denoising methods. 
\end{abstract}
%Though these methods are very effective in Gaussian noise removal, the noise in real images are signal dependent and more complex than Gaussian noise. Therefore, only exploiting the external or internal priors are not enough for real image denoising.

@@

We compare the above mentioned methods on the 60 cropped images from \cite{crosschannel2016}. The average PSNR and speed of these methods are listed in Table \ref{tab1}. It can be seen that our proposed method achieves better PSNR results than the methods of "External" and "Internal". The speed of our proposed method is much faster than the "Internal" method while only a little slower than the "External" method. We also compare the visual quality of the denoised images by these methods. From the results listed in Figure \ref{fig2} and Figure \ref{fig3}, we can see that the "External" method is good at recovering structures (Figure \ref{fig2}) while the "Internal" method is good at recovering internal complex textures (Figure \ref{fig3}). And by utilizing both the external and internal priors, our proposed method can recover well both the structures and textures. Noted that the noisy images in Figures \ref{fig2} and \ref{fig3} are cropped from the same image captured by Nikon D600 at ISO $=3200$ in \cite{crosschannel2016}. Hence, the differences on PSNR and visual quality among these methods only depends on the contents of the cropped images.

\begin{table}
\caption{Average PSNR (dB) results and Run Time (seconds) of the External, the Internal, and our proposed methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
\label{tab1}
\vspace{-3mm}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|}
\hline
 & \textbf{Noisy} &\textbf{External} &\textbf{Internal} &\textbf{Ours}  
\\
\hline
PSNR & 34.51 & 38.21 & 38.07 & \textbf{38.75} 
\\
\hline
Time & | &  \textbf{56.39}  & 706.63 & 58.47
\\
\hline
\end{tabular}
\end{center}\vspace{-6mm}
\end{table}
